\documentclass[14pt]{lhcbnote}
\usepackage[toc,page]{appendix}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{xcolor,colortbl}

\title{L1Topo Programming Model}
\author{Various {\address[BGADD]{J.G.Universiteat Mainz,Germany}}
%\author{Andreas Ebling{\address[BGADD]{J.G.Universiteat Mainz,Germany}}
%\author{Eduard Simioni{\address[BGADD]{J.G.Universiteat Mainz,Germany}}
%with a different address
%New Author{\address[NEWADD]{His address}%
%with the same address
%Other Author{\addressmark[BGADD]}}
}

\doctyp{Technical Note}
\dociss{1}
\docrev{0}
\docref{}
\doccre{February 13, 2014}
\docmod{\today}
\usepackage{float}
\restylefloat{table}

\begin{document}

\section{Abstract}
L1Topo is a new L1 Trigger subsystem consisting of 
a single ATCA crate initially equipped with two (max three) ATCA modules. 
L1Topo register definition is here defined.
U. Schaefer, J. Schaffer, M. Simon, S. Artz, M. Palka, G. Korcyl, C. Kahra,
and E. Simioni etc....

%\maketitle
%The registers name and address are defined in Tabs.\ref{tab_top_reg},\ref{tab_low_reg}. The full register name will be in the following format:
%\begin{center}
%L1Topo[x].U[y].[RegisterName],
%\end{center}
%where:
%\begin{itemize}
%\item [x] = 1,2,3 (L1Topo board).
%\item [y] = 1,2,3 (FPGA). U1 and U2 are the processor FPGAs and U3 is the control FPGA.
%\end{itemize}
%
\section{L1Topo Register Map}
The register map is identical for all L1Topo modules with their firmware variants. It contains addresses
managed by IPbus link with address space per FPGAs. 

\begin {table}[H]
\begin{center}
\caption {FPGAs addresses}
\label{top_level_addresses}
\begin{tabular}{|l|l|l|}
\hline
address(hex) & FPGA  & Function\\
\hline
0x00000000 & Processor\_U3 & Control \\
0x80000000 & Processor\_U1 & Topo Algorithms processor \\
0xC0000000 & Processor\_U2 & Topo Algorithms processor \\
\hline
\end{tabular}
\end{center}
\end{table}

In this document the definition of the registers address follow the hierarchy in Tab.\ref{top_level_addresses}. 
Sect.\ref{section_1} describes the registers definition for the Control FPGA. Sect.\ref{section_2} 
and \ref{section_3} describes the registers definition for the algorithms processors FPGA.
Sub-spaces are further defined.\\
The definiton of registers follow the L1Calo guidelines.

% Control FPGA registers space
\include{sections/section1}

% U1 registers space
\include{sections/section2}

% U2 registers space
\include{sections/section3}
%
\end{document}

